network_plot

### 2025-01-20 R/run_first/1.pattern_examples_MASCARA_pipeline.Rmd
25_01_20
MILP arc consistency KEGG network

sim_data <- Create_Core_DEV_2(nreps = 3, meta = meta, 
                        EffectSize = c(X_a_ab = 5, time = 1, E = 10, mu = 1, Struc_E = 1),    # E = 1, Struc_E = 0.4
                        struc_resid = TRUE, e_sigma = c(1.5,0.8,0.0), a_sigma = c(1,0.7,0.6,0.1),
                        b_sigma = c(1,0.9), irr_spikes = TRUE, SCORE_SEED = 12, Experiment_responders = Experiment_responders,
                        struc_seed = 127, score_plot = FALSE, plot = FALSE)

@@

a <- ggplot(scores_r_baits, aes(x = Comp_1, y = Comp_2)) +
  geom_point(aes(colour = growth_condition, shape = time, size = 20)) +
  ggtitle("Scores") + 
  theme_bw()

colnames(yloadings) <- colnames(loadings_r_baits)

@@

```{r}
loadings_r_baits$ID[-which(loadings_r_baits$ID %in% c(baits,spikes))] <- "Other"

loadings_r_baits$ID[which(loadings_r_baits$ID %in% spikes)] <- "Spikes"
loadings_r_baits$ID[which(loadings_r_baits$ID %in% baits)] <- "Baits"
```

@@

  geom_segment(x = 0, y = 0, xend = line[1], yend = line[2], lineend = "round", linewidth = 2, colour = "purple", arrow = arrow()) +    
  scale_shape_manual(values=c(3, 16, 17))+

    scale_color_manual(values=c('#E69F00',"black", '#56B4E9'))+
      geom_point(data = loadings_r_baits[which(loadings_r_baits$ID %in% c("Baits","Spikes")),], aes(size = 15)) +
  theme_bw()

b
```

>>>>

sim_data <- Create_Core_DEV_2(nreps = 3, meta = meta, 
                        EffectSize = c(X_a_ab = 5, time = 1, E = 5, mu = 1, Struc_E = 0.9),    # E = 1, Struc_E = 0.4
                        struc_resid = TRUE, e_sigma = c(1.5,0.8,0.0), a_sigma = c(1,0.7,0.6,0.1),
                        b_sigma = c(1,0.9), irr_spikes = TRUE, SCORE_SEED = 12, Experiment_responders = Experiment_responders,
                        struc_seed = 1230, score_plot = FALSE, plot = FALSE)

@@

a <- ggplot(scores_r_baits, aes(x = Comp_1, y = Comp_2)) +
  geom_point(aes(colour = growth_condition, shape = time, size = 20)) +
    scale_shape_manual(values=c(18,19,20,21))+  #3, 16, 17

  guides(size = FALSE) +
  ggtitle("Residual Scores") + 
  theme_bw()
```

```{r}
colnames(yloadings) <- colnames(loadings_r_baits)

@@

```{r}
loadings_r_baits$ID[-which(loadings_r_baits$ID %in% c(baits,spikes))] <- "Unrelated"
set.seed(213)
loadings_r_baits$ID[which(loadings_r_baits$ID %in% spikes)] <- sample(c("Pathway","Related"),length(which(loadings_r_baits$ID %in% spikes)),replace = T)
loadings_r_baits$ID[which(loadings_r_baits$ID %in% baits)] <- "Baits"

# sample(loadings_r_baits$ID[which(loadings_r_baits$ID == "Pathway")],6) <- "Related"
```

@@

  geom_segment(x = 0, y = 0, xend = line[1], yend = line[2], lineend = "round", linewidth = 2, colour = "steelblue", arrow = arrow()) +    
  scale_shape_manual(values=c(17,16,16,15))+  #3, 16, 17

    scale_color_manual(values=c('purple',  'purple',"orange","lightgreen"))+
      geom_point(data = loadings_r_baits[which(loadings_r_baits$ID %in% c("Baits","Pathway","Related")),], aes(size = 15)) +
    guides(size = FALSE) +

  theme_bw()

a + b
```

### 2025-01-20 R/run_first/2.plot_pathway_net_example.Rmd
25_01_20
MILP arc consistency KEGG network

Net <- V(g)$name
```

```{r}
id <- c(1:length(Net))

@@

Net[which(Net %in% baits)] <- "POI"
Net[which(Net %in% spikes)] <- "RP"

Net[-which(Net %in% c("POI","RP"))] <- "URP"

@@

Gene <- names(V(g))
Gene[-which(Gene %in% temp)] <- "Other"
Gene[which(Gene %in% temp)] <- "Baits"

@@

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Net = Net)

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Gene = Gene)

@@

colours = c("POI" = "purple", "RP" = "orange", "URP" = "lightgreen")

@@

edge_colours <- c("+ve" = "grey", "-ve" = "blue")

@@

realplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) +  
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = Net, shape = Gene), show.legend=FALSE        #CHANGE THIS
  ) +
  geom_node_point(
    aes(color = Net, shape = Gene)    #, shape = Baits
  ) +
  scale_color_manual(values = colours) + 
    scale_shape_manual(values = c(17,16)) +   #18,20

@@

adj[Net == "URP", Net == "URP"]  <- 1
adj[Net %in% c("POI","RP"), Net %in% c("POI","RP")] <- 1

adj[Net %in% c("POI","RP"), Net == "URP"] <- -1
adj[Net == "URP", Net %in% c("POI","RP")] <- -1
```

@@

#define correctly ordered type Net
Net <- V(g)$name

@@

```{r}
id <- c(1:length(Net))

@@

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Net = Net)

colours = c("POI" = "purple", "RP" = "orange", "URP" = "lightgreen")  
# shape = c("Baits" = 18, "other" = 1)
edge_colours <- c("+ve" = "black", "-ve" = "grey")

@@

badplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) +   #, linetype = "dashed"
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = Net, shape = Gene), show.legend=FALSE
  ) +
  geom_node_point(
    aes(color = Net, shape = Gene)
  ) +
  scale_color_manual(values = colours) + 
      scale_shape_manual(values = c(17,16)) +   #18,20
  # scale_edge_linetype_manual(values = "dashed") +

>>>>

Pathway  <- V(g)$name
```

```{r}
id <- c(1:length(Pathway ))

@@

Pathway [which(Pathway  %in% baits)] <- "POI"
Pathway [which(Pathway  %in% spikes)] <- "Related"

Pathway [-which(Pathway  %in% c("POI","Related"))] <- "Unrelated"

@@

Feature <- names(V(g))
Feature[-which(Feature %in% temp)] <- "Other"

Feature[which(Pathway  %in% c("POI","Related"))] <- "Targets"

Feature[which(names(V(g)) %in% temp)] <- "Baits"

Feature <- factor(Feature, levels = c("Baits","Targets","Other"))

# Feature[which(names(V(g)) %in% spikes)] <- "Targets"

@@

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Pathway  = Pathway )

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Feature = Feature)

@@

colours = c("POI" = "purple", "Related" = "orange", "Unrelated" = "lightgreen")

@@

edge_colours <- c("+ve" = "#091EB7", "-ve" = "blue")

@@

realplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association), show.legend=FALSE) +  
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = Pathway , shape = Feature), show.legend=FALSE        #CHANGE THIS
  ) +
  geom_node_point(
    aes(color = Pathway , shape = Feature)    #, shape = Baits
  ) +
  scale_color_manual(values = colours) + 
    scale_shape_manual(values = c(17,16,15)) +   #18,20

@@

adj[Pathway  == "Unrelated", Pathway  == "Unrelated"]  <- 1
adj[Pathway  %in% c("POI","Related"), Pathway  %in% c("POI","Related")] <- 1

adj[Pathway  %in% c("POI","Related"), Pathway  == "Unrelated"] <- -1
adj[Pathway  == "Unrelated", Pathway  %in% c("POI","Related")] <- -1
```

@@

#define correctly ordered type Pathway 
Pathway  <- V(g)$name

@@

```{r}
id <- c(1:length(Pathway ))

@@

tidynet <- tidynet %>%
  activate(nodes) %>%
  mutate(Pathway  = Pathway )

colours = c("POI" = "purple", "Related" = "orange", "Unrelated" = "lightgreen")  
# shape = c("Baits" = 18, "other" = 1)
edge_colours <- c("+ve" = "black", "-ve" = "grey")

@@

badplot <- ggraph(tidynet, layout = coords) + 
  geom_edge_link(aes(colour = association, alpha = weight), show.legend=FALSE) +   #, linetype = "dashed"
  scale_edge_color_manual(values = edge_colours, guide = "none") +
  geom_node_point(
    aes(size = VIP, color = Pathway , shape = Feature), show.legend=FALSE
  ) +
  geom_node_point(
    aes(color = Pathway , shape = Feature)
  ) +
  scale_color_manual(values = colours) + 
      scale_shape_manual(values = c(17,16,15)) +   #18,20
  # scale_edge_linetype_manual(values = "dashed") +
